---
 output:
   md_document:
     variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
  
# Overview 

`gabaclassifier` classifies a given neuronal morphology into one of eight types (see below), such as Chandelier or Martinotti. 

For example, it classifies cell C030502A as a nest basket cell.

```{r, message=FALSE}
library(gabaclassifier) 
file <- system.file('extdata', 'C030502A.swc', package = 'gabaclassifier')
classify_interneuron(file = file, layer  = '23')
``` 

The output is short code for the type name. The codes for the eight types are: 
```{r, echo=FALSE}
knitr::kable(data.frame(short = get_type_codes(), long = get_type_names())  )
```  

# Installing   

`gabaclassifier` requires `neurostr` and `neurostrplus` to be installed. The following installs all three packages (install the `devtools` package with `install.package('devtools')` if you don't have it):
```{r, eval = FALSE}
# install.package('devtools')
devtools::install_github("ComputationalIntelligenceGroup/neurostrr")
devtools::install_github("ComputationalIntelligenceGroup/neurostrplus")
devtools::install_github("ComputationalIntelligenceGroup/gabaclassifier") 
```   
These packages have only been tested on Ubuntu 16.04.    

# Usage
Cells are classified with the `classify_interneuron` function. The inputs are

- A path to a SWC reconstruction of a neuron morphology 
- The layer containing the cell's soma 

The path must be fully expanded, that is `/home/user/neuron.swc` will work while `~/neuron.swc` will not. 

The model has been trained with layer L2/3 to layer L6 interneurons and thus only interneurons from those layers are allowed as input to `classify_interneuron`.  
```{r} 
classify_interneuron(file = file, layer  = '1')
```
 
`gabaclassifier` will only classify a morphology reconstruction that passes the following quality checks:

- Has both axon and dendrites 
- The axon is not interrupted
- Has a soma
- Nerites are attached to soma 
- Axonal length > 3000 micrometers 

So, it will not classify the following cell:
```{r}  
file <- system.file('extdata', 'C170501A2.swc', package = 'gabaclassifier')
classify_interneuron(file = file, layer  = '4')
```

The underlying model has been trained and tested with rat somatosensory cortex interneurons (see below). Classifying interneurons from other species, brain area etc. may be less reliable.
  
# Model  
The classification is based on a model trained in a supervised fashion. The model is a random forest with 2000 trees trained on `r length(gabaclassifier:::cell_ids)` cells with `r length(gabaclassifier:::features)` morphometrics for each. The morphometrics were computed with the `neuorstrplus` and `neurostr` packages. All cells are hind-limb somatosensory cortex interneurons from two-week-old male Wistar rats reconcstructed by the Markam laboratory. The ids of the cells are available with `gabaclassifier:::cell_ids`. The cells are from layers L2/3, L4, L5, or L6 cell and fullfill the above-listed morphology quality criteria.  

The 10-fold cross-validated accuracy of the model is `r sum(diag(gabaclassifier:::confusion_matrix)) / sum(gabaclassifier:::confusion_matrix)`. The types with highest sensitivity are Martinotti, Large basket, and nest basket. The model in unable to recognizes bitufted cells. 
```{r, echo = FALSE}
knitr::kable(gabaclassifier:::confusion_matrix)
```

