---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# gabaclassifier

The goal of gabaclassifier is to ...

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
``` 


# Installing  
It is straightforward from Github. `gabaclassifier` requires  `neuroimm`, `neurostrr` to be installed from Github. 
- DEPENDS ON PKG neurostrplus and neurostr. 
- Intstall those via github   

```{r, eval = FALSE}
devtool::install_github()
devtool::install_github()
``` 
It has only been tested on Ubuntu 16.04.  

# Issues
- **pkg descrption** 
- **Maybe also include the training functions here, also the trainig dataset, with the list of used cells.**
- check package docs
- **apply theta_complement? maybe it could change the results a lot!!** does it just apply to torque?
- Update description
- Poner detalles sobre el modelo y su accuracy
- Add morphology validation and checks. Filters for not suitable. 
- Anadir neuronas de ejemplo 
- Anadir vignette con ejemplos de uso 

# TOdo neurostr
- NeuroSTR: the expanded path bug
- CORREGIR EL NOMBRE DE LA NEURON EN NEUROSTRCPP. En la fila de NEUROSTRCPP.  
