---
title: "GABAergic interneurons classifier"
author: "Bojan Mihaljevic"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Input 
- A SWC/**ASC/DAT** reconstruction of a neuron morphology
- The layer containing that cell [optional]  [**not done yet**]

The layer information corresponds to male rat ... somatosensory cortex. If the cells corresponds to very different laminar distribution data, then the layer should be omitted and related morphometrics will not be computed. It is important that the morphology is of sufficient quality, as `gabaclassifier` does not perform any checks.

# Installing 

It is straightforward from Github. `gabaclassifier` requires  `neuroimm`, `neurostrr` to be installed from Github. 

```{r, eval = FALSE}
devtool::install_github()
devtool::install_github()
```

Currently it only **works on linux.** 

# Model 
A random forest trained on 217 ... 

An one-versus-all combination of random forest models provides somewhat better models for under-represented types. The accuracy is 72%. **Show the confusion matrix.**
The data and model building is explained in paper...Try oversampling? Not easy in multiclass.  No feature selection currently (OK with random forest).    

# Usage 

```{r}
library(gabaclassifier)
path <- ''
layer <- '23'
# classify_interneuron(path, layer )
```
Allowed values for layer are...(character)
The types are MC = martinotti etc. ...   

# Future work  
- Basic morphology checks, such as axonal length, to perform before classifying an interneuron. 
