---
title: "GABAergic interneurons classifier"
author: "Bojan Mihaljevic"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Input 
- A cell from rat somatosensory cortex. Otherwise, many variables will be useless. Alternative: provide a logical parameter and then omit those features. 
- The layer containing that cell. Also could be optional. 

# Documentation
- pre-requisites: just linux
- Vignette describing the process and what is done 
- Describe that there are no checks currently

# Model 
An one-versus-all combination of random forest models. We also tried a straghtforward random forest. Could we select one just like that?

The accuracy is 70%. Show the confusion matrix. Simple RF is 71% accuracy. No improvement. Did we also do oversampling? Mention the original paper or not?
0.7188940 plain random forest without any sampling or anything. The data and model building is explained in paper...


# Overview
- Input
- Checks
- Compute features
- Classify 

# Usage 

```{r}
library(gabaclassifier)
path <- ''
layer <- '23'
classify_interneuron(path, layer )
```
Allowed values for layer are...(character)
The types are MC = martinotti etc. ...  
